Sequential rank agreement methods for comparison of ranked lists

### 2016-05-25 latex/superranker-manuscript.tex
minor adjustments

We now define the parameter of interest. For any given threshold value $q$, 
a change-point $d^\ast(q)$ in the list agreement is defined by
\begin{equation}
  d^\ast(q) = \argmin_{d\in\{1,\dots,P\}}\textrm{sra}(d)>q.
\end{equation}
The value of $q$ could for example be the agreement of randomly
permuted lists. The corresponding estimated change-point is similarly defined by
\begin{equation}
\widehat{d^\ast_L}(q) = \argmin_{d\in\{1,\dots,P\}}\widehat{\textrm{sra}}_L(d)>q
\end{equation}
The consistency of $\widehat{d^\ast_L}(q)$ then follows by a simple corollary.

@@

We start by defining the following counting process
\begin{align}
  N(p; d) = \sum_{s=1}^p 1\left(Q(R(X_s) \leq d) > 0\right), \quad p = 1,\ldots, P
\end{align}
which runs through the list elements in an arbitrary order and counts
how many list elements have a strictly positive probability to have
rank less than or equal to $d$ under the probability measure $Q$.
Note that the cardinality of the set $S(d)$ in equation
(\ref{eq:sumset}) is equal to the counting process evaluated at the last element:
\begin{equation*}
  |S(d)| = N(P;d).
\end{equation*}

@@

The sequential rank agreement given in equation
(\ref{def:sra}) may therefore be rewritten as the following integral
with respect to $N$
\begin{align}
  \textrm{sra}(d) = \int_{1}^P \frac{A(X_p)}{N(P; d)}\mathrm dN(p; d).
\end{align}
The empirical sequential rank agreement is similarly given by
\begin{align}
  \widehat{\textrm{sra}}_L(d) &= \int_1^P \frac{\widehat{A}_L(X_p)}{\widehat{N}_L(P; d)}\mathrm d \widehat{N}_L(p; d) 
\end{align}
and it follows that
\begin{align}
  \sup_{d \in 1,\ldots,P}\left|\widehat{\textrm{sra}}_L(d) - \textrm{sra}(d)\right| \leq \sup_{d \in 1,\ldots,P}\left|U_L(d)\right| - \sup_{d \in 1,\ldots,P}\left|V_L(d)\right|
\end{align}
where
\begin{align}
  U_L(d) &= \int_1^P\frac{A(X_p)}{N(P;d)} \mathrm d\left(\widehat{N}_L(p; d) - N(p; d)\right)\\
  V_L(d) &=  \int_1^P \left(\frac{\widehat{A}_L(X_p)}{\widehat{N}_L(P; d)} - \frac{A(X_p)}{N(P;d)}\right)\mathrm d\widehat{N}_L(p; d)
\end{align}
The conclusion of the proof therefore follows if each of these two
terms are uniformly of order $o_P(1)$ in $d$.  For the first term we
have that
\begin{align}
  \left|U_L(d)\right| \leq \left(\sup_{p \in 1,\ldots,P}\left|\frac{A(X_p)}{N(P;d)}\right|\right)\left(\widehat{N}_L(p; d) - N(p; d)\right)\biggr\rvert_1^P
\end{align}
where the second factor is $o_P(1)$ uniformly in $d$ by equation
(\ref{eq:countingConv}). The first factor is $O(1)$ since $N(P;d)>0$
uniformly in $d$ and because $A(X_p)\le 2L^2$ u uniformly in $p$. . It
thus follows that $\left|U_L(d)\right| = o_P(1)$ uniformly in $d$.

>>>>

We now define the parameter of interest. For any given threshold value $q$, 
a change-point $d^\ast(q)$ in the list agreement is defined by
\begin{equation}
  d^\ast(q) = \min\left\{\argmin_{d\in\{1,\dots,P\}}\textrm{sra}(d)>q, P\right\}.
\end{equation}
The value of $q$ could for example be the agreement of randomly
permuted lists. The corresponding estimated change-point is similarly defined by
\begin{equation}
\widehat{d^\ast_L}(q) = \min\left\{\argmin_{d\in\{1,\dots,P\}}\widehat{\textrm{sra}}_L(d)>q, P \right\}
\end{equation}
The consistency of $\widehat{d^\ast_L}(q)$ then follows by a simple corollary.

@@

We start by defining the following cadlag function
\begin{align}
  N(p; d) = \sum_{s=1}^p 1\left(Q(R(X_s) \leq d) > 0\right), \quad p = 1,\ldots, P
\end{align}
which runs through the list elements in an arbitrary order and counts
how many list elements have a strictly positive probability to have
rank less than or equal to $d$ under the probability measure $Q$.
Note that the cardinality of the set $S(d)$ in equation
(\ref{eq:sumset}) is equal to the counting process evaluated at the last element:
\begin{equation*}
  |S(d)| = N(P;d).
\end{equation*}

@@

The sequential rank agreement given in equation
(\ref{def:sra}) may therefore be rewritten as the following integral
with respect to $N$
\begin{align}
  \textrm{sra}(d) = \int_{1}^P \frac{A(X_p)}{N(P; d)}\mathrm dN(p; d).
\end{align}
The empirical sequential rank agreement is similarly given by
\begin{align}
  \widehat{\textrm{sra}}_L(d) &= \int_1^P \frac{\widehat{A}_L(X_p)}{\widehat{N}_L(P; d)}\mathrm d \widehat{N}_L(p; d) 
\end{align}
and it follows that
\begin{align}
  \sup_{d \in 1,\ldots,P}\left|\widehat{\textrm{sra}}_L(d) - \textrm{sra}(d)\right| \leq \sup_{d \in 1,\ldots,P}\left|U_L(d)\right| - \sup_{d \in 1,\ldots,P}\left|V_L(d)\right|
\end{align}
where
\begin{align}
  U_L(d) &= \int_1^P\frac{A(X_p)}{N(P;d)} \mathrm d\left(\widehat{N}_L(p; d) - N(p; d)\right)\\
  V_L(d) &=  \int_1^P \left(\frac{\widehat{A}_L(X_p)}{\widehat{N}_L(P; d)} - \frac{A(X_p)}{N(P;d)}\right)\mathrm d\widehat{N}_L(p; d)
\end{align}
The conclusion of the proof therefore follows if each of these two
terms are uniformly of order $o_P(1)$ in $d$.  For the first term we
have that
\begin{align}
  \left|U_L(d)\right| \leq \left(\sup_{p \in 1,\ldots,P}\left|\frac{A(X_p)}{N(P;d)}\right|\right)\left(\widehat{N}_L(p; d) - N(p; d)\right)\biggr\rvert_1^P
\end{align}
where the second factor is $o_P(1)$ uniformly in $d$ by equation
(\ref{eq:countingConv}). The first factor is $O(1)$ since $N(P;d)>0$
uniformly in $d$ and because $A(X_p)\le 2P^2$ u uniformly in $p$ \mcomment{double check bound}. It
thus follows that $\left|U_L(d)\right| = o_P(1)$ uniformly in $d$.
